Geospatial and Temporal Analysis of Toronto's Cycling Infrastructure

### 2024-09-27 paper/paper.qmd
paper final draft

The structure of this paper is organized as follows: @sec-data presents the data sources and methodologies, followed by an overview of the results in @sec-res. The findings are then discussed in @sec-dis, and additional detailed information is provided in the appendix at @sec-app.

@@

# Results {#sec-res}

## Data Trend

@@

## Distributions

@@

## Maps

>>>>

The structure of this paper is organized as follows: @sec-data presents the data sources, methodologies, and the visualization of the results. The findings are then discussed in @sec-dis, and additional detailed information is provided in the appendix at @sec-app.

@@

## Charts

### Data Trend

@@

### Distributions

@@

### Maps
